### 2019-09-12 paper/paper.tex
Update paper.tex

\section{Bayesian adaptive trial design and sequential analysis}
The Bayesian machinery described above can be employed to perform adaptive trial design and sequential analysis of RCTs. In this context, the Bayesian approach offers the advantage of no statistical requirement for a stopping rule. Though other reasons for a stopping rule are important, such as funding and avoiding bias due to stopping when a test critical value is just reached, a sequential analysis minimizes costs, time and the number of patients exposed to inferior treatment. Further, there is no satisfactory frequentist differences of differences analysis without restrictive assumptions. The analytical sampling distributions are unknown and intractable; asymptotic assumptions are invalid with small samples; and there may be other constraints (e.g., boundary conditions). Bootstrapping is also inferior due to the small sample sizes. The commonly used Welch t-test represents an ad hoc attempt to deal with different variances across samples that does not perform well in simulations\cite{Mills2019}.  Importantly, these issues are resolved by the Bayesian machinery.
\vskip 6pt
In previous work\cite{Strawn2018,Mills2019}, data from a federally-funded NIH trial of pediatric anxiety disorders (Child/Adolescent Anxiety Multimodal Study [CAMS], N=488) were analyzed to validate the proposed methodology and to examine treatment and placebo responses. In CAMS, youth, aged 7-17 (mean age: 10.7 years) with generalized, separation and$/$or social anxiety disorders, were randomized (2:2:2:1) to cognitive behavioral therapy (CBT, n=139), a selective serotonin reuptake inhibitor (SSRI), sertraline (SRT, n=133), SRT+CBT (n=140), or pill placebo (PBO, n=76).
% insert pars_difference_sequential.png
% pars_difference_sequential.png
\vskip 6pt
The following example sequentially analyzes the data for the combined treatment SRT+CBT relative to PBO using Bayesian updating.  To evaluate the hypothesis in (\ref{eq:hoh1}) where $\mu_1$ is the ATE of SRT+CBT and $\mu_2$ is the ATE of PBO. Starting with a sample of 12 (8 treated, 4 placebo), the posterior density was updated with each additional 6 observations (4 treated:2 placebo).  The sequence of posteriors as $n$ is increased for the difference in ATE between SRT+CBT and PBO is shown in Figure~\ref{fig:pars_diff}, and the PDR giving posterior odds against the null hypothesis (\ref{eq:odds}), posterior probability that the difference is greater than zero (\ref{eq:pval}), and two sided $p$-value ($\approx 2\times p(\delta \ge 0)$) are given in Table \ref{tab:seq}.
\begin{table}
	\tbl{Evidence Against $H_0$:$\delta=0$}{
		\begin{tabular}{rrrr} %\hline
			$n$   & $PDR(\delta = 0)$ & P$(\delta \ge 0)$ & $p$-value \\
			18  & 1.37       & 0.2382      & 0.4763  \\
			36  & 1.19       & 0.2887      & 0.5775  \\
			54  & 3.49       & 0.0625      & 0.1250  \\
			72  & 61.35      & 0.0025      & 0.0051  \\
			90  & 572.96     & 0.0003      & 0.0005  \\
			108 & 1083.5    & 0.0001       & 0.0002  \\
			126 & 329.24     & 0.0005      & 0.0010  \\
			144 & 610.67     & 0.0002      & 0.0004  \\
			162 & 4596.8    & 0.0000       & 0.0000   \\
			180 & 2394.6    & 0.0000       & 0.0000   \\
			198 & 46452.9   & 0.0000       & 0.0000    
	\end{tabular}}
	\label{tab:seq}
\end{table}

\begin{figure}[t]
	\centerline{\includegraphics[width=8cm]{sequential_plot.pdf}}
	\caption{Difference in ATE between treatment and placebo groups.} 
	\label{fig:pars_diff}
\end{figure}

>>>>

\section{Bayesian adaptive trial design and sequential analysis}
The Bayesian machinery described above can be employed to perform adaptive trial design and sequential analysis of RCTs. In this context, the Bayesian approach offers the advantage of no statistical requirement for a stopping rule. Though other reasons for a stopping rule are important, such as funding and avoiding bias due to stopping when a test critical value is just reached, a sequential analysis minimizes costs, time and the number of patients exposed to inferior treatment. Further, there is no satisfactory frequentist differences of differences analysis without restrictive assumptions. The analytical sampling distributions are unknown and intractable; asymptotic assumptions are invalid with small samples; and there may be other constraints (e.g., boundary conditions). Bootstrapping is also inferior due to the small sample sizes. The commonly used Welch t-test represents an ad hoc attempt to deal with different variances across samples that does not perform well in simulations\cite{Mills2019}.  Importantly, these issues are resolved by the Bayesian machinery.
\vskip 6pt
In previous work\cite{Strawn2018,Mills2019}, data from a federally-funded NIH trial of pediatric anxiety disorders (Child/Adolescent Anxiety Multimodal Study [CAMS], N=488) were analyzed to validate the proposed methodology and to examine treatment and placebo responses. In CAMS, youth, aged 7-17 (mean age: 10.7 years) with generalized, separation and$/$or social anxiety disorders, were randomized (2:2:2:1) to cognitive behavioral therapy (CBT, n=139), a selective serotonin reuptake inhibitor (SSRI), sertraline (SRT, n=133), SRT+CBT (n=140), or pill placebo (PBO, n=76).
% insert pars_difference_sequential.png
% pars_difference_sequential.png
\vskip 6pt
The following example sequentially analyzes the data for the combined treatment SRT+CBT relative to PBO using Bayesian updating.  To evaluate the hypothesis in (\ref{eq:hoh1}) where $\mu_1$ is the ATE of SRT+CBT and $\mu_2$ is the ATE of PBO. Starting with a sample of 12 (8 treated, 4 placebo), the posterior density was updated with each additional 6 observations (4 treated:2 placebo).  The sequence of posteriors as $n$ is increased for the difference in ATE between SRT+CBT and PBO is shown in Figure~\ref{fig:pars_diff}, and the PDR giving posterior odds against the null hypothesis (\ref{eq:odds}), posterior probability that the difference is greater than zero (\ref{eq:pval}), and two sided $p$-value ($\approx 2\times p(\delta \ge 0)$) are given in Table \ref{tab:seq
\begin{figure}[t]
	\centerline{\includegraphics[width=8cm]{sequential_plot.pdf}}
	\caption{Difference in ATE between treatment and placebo groups.} 
	\label{fig:pars_diff}
\end{figure}

\begin{table}
	\tbl{Evidence Against $H_0$:$\delta=0$}{
		\begin{tabular}{rrrr} %\hline
			$n$   & $PDR(\delta = 0)$ & P$(\delta \ge 0)$ & $p$-value \\
			18  & 1.37       & 0.2382      & 0.4763  \\
			36  & 1.19       & 0.2887      & 0.5775  \\
			54  & 3.49       & 0.0625      & 0.1250  \\
			72  & 61.35      & 0.0025      & 0.0051  \\
			90  & 572.96     & 0.0003      & 0.0005  \\
			108 & 1083.5    & 0.0001       & 0.0002  \\
			126 & 329.24     & 0.0005      & 0.0010  \\
			144 & 610.67     & 0.0002      & 0.0004  \\
			162 & 4596.8    & 0.0000       & 0.0000   \\
			180 & 2394.6    & 0.0000       & 0.0000   \\
			198 & 46452.9   & 0.0000       & 0.0000    
	\end{tabular}}
	\label{tab:seq}
\end{table}
